---
title: "try"
author: "kaji331"
date: "2017年8月1日"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Trying machine learning by caret, mlr, SuperLearner and H$_2$O

### Now, I will try the caret package for classification of iris dataset by different methods. Because of different parameters and different ideas, I should test different learners respectively.

> Bagging and Boosting are two kind of meta-algorithms for learners

> Bagging: One classifier for different subset of training data by bootstrap, reducing errors from noise, bias and variance (eg. Random forest, Bagged decision trees, CART and so on, not effetive for nearest neighbors)

> Boosting: One training data for different tries of a weak learner, improving some weak learner better than bagging (eg. AdaBoost)

adaboost: AdaBoost Classification Trees, from fastAdaboost
```{r caret}
library(caret)
library(mlbench)
set.seed(1984)
train <- iris
testing <- iris
for (p in c("pca","center","scale",c("center","scale"),c("pca","scale"))) {
  for (s in c("boot","optimism_boot","cv","repeatedcv")) {
    ctrl <- trainControl(method=s,number=100,classProbs=T)
    fit <- train(Species ~ .,data=train,method=m,preProcess=p,tuneLength=15,trControl=ctrl,
                 metric="Accuracy")
    pre <- predict(fit,newdata=testing)
    print(c(m,p,s))
    print((temp == iris$Species) %>>% table)
  }
}
```

amdai: Adaptive Mixture Discriminant Analysis, from adaptDA
AdaBag: Bagged AdaBoost, from adabag, plyr
treebag: Bagged CART, from ipred, plyr, e1071
bagFDA: Bagged Flexible Discriminant Analysis, from earth, mda
bagEarth: Bagged MARS, from earth
bag: Bagged Model, from caret
bartMachine: Bayesian Additive Regression Trees, from bartMachine
glmboost: Boosted Generalized Linear Model, from plyr, mboost
bstSm: Boosted Smoothing Spline, from bst, plyr
C5.0: C5.0, from C50, plyr
chaid: CHi-squared Automated Interaction Detection, from CHAID
cforest: Conditional Inference Random Forest, from party
ctree: Conditional Inference Tree, party
vglmContRatio: Continuation Ratio Model for Ordinal Data, from VGAM
